Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-07-16 MainText.Rmd
writing abstract

>>>>

With global climate change, extreme climatic events (ECEs) appear to be more common than usual. These ECEs 
could pose severe impact on the resistance or resilience of a population or community level through
life-history traits of the species. Therefore predicting the impact of ECEs 
on extinction risk of a population is necessery. We here introduced the potential use of "tail-dependence" 
property of a copula in modelling the extinction risk of an age-structured single patch model. We also 
extended the generalized findings of density-independent metapopulation model from [@Ghosh_copula] 
to density-dependence metapopulation models with this copula approach. For metapopulation models, 
we showed extinction risk not only depended on the nature of tail-dependence of spatially correlated 
noise but was also influenced by the inherent dynamics of the population-model.
